### 2008-09-18 doc/client/client_technical.tex
Fix some PDF stuff

\documentclass{book}
%\documentclass{article}           %for shorter notes
\usepackage{graphicx}              %for PNG images (pdflatex)
%\usepackage{graphics}              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref}  %for \url tag
\usepackage{color}                 %for defining custom colors
\usepackage{framed}                %for shaded and framed paragraphs
\usepackage{textcomp}              %for various symbols, e.g. Registered Mark
\usepackage{geometry}              %for defining page size
\usepackage{longtable}             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Paper author},
  pdftitle = {Paper title},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\arclib}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

>>>>

\documentclass{book}
%\documentclass{article}           %for shorter notes
\usepackage{graphicx}              %for PNG images (pdflatex)
%\usepackage{graphics}              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref}  %for \url tag
\usepackage{color}                 %for defining custom colors
\usepackage{framed}                %for shaded and framed paragraphs
\usepackage{textcomp}              %for various symbols, e.g. Registered Mark
\usepackage{geometry}              %for defining page size
\usepackage{longtable}             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Mattias Ellert, Bjarte Mohn, Ivan Marton, Gabor Roczei},
  pdftitle = {libarcclient},
  pdfsubject = {A Client Library for ARC},
  pdfkeywords = {ARC,client,library},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\arclib}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}
